---
title: "R Notebook"
output: html_notebook
---

# Load libbraries    
The first thing we need to do is load the libraries.  

```{r libraries}
library(tidyverse)
library(readxl)
```


# Load the data and save it as eco.df   
the next thing we need to do is load the data and get it to a dataframe called
eco.df   

```{r load.data}
eco.df <- read_excel("block2_CR_0-2_10172021.xlsx") 
  
# call file to see
eco.df
```


```{r}
names(eco.df)
```


# Clean up the data and fix a few things     
We need to remove variable 14 how would we do that?   
remember the verb is select and we want to remove something   
its called "...14" as it is the 14th position and can remove that column by
number as well but can be more dangerous.    
```{r}
 eco.df <- eco.df %>%  
  
```


now we need to rename column 1 as letter - how is that done using the rename
verb
```{r}
 eco.df <- eco.df %>% 
 
```

# Rearragne the dataset so we can work it    
now we need to change the data so we can work with it... what do we have to do and 
how do we do it.

We are going to use the verb pivot_longer and we are going to leave cols along 
cols = -c(letter)
names_to="number"
values_to = "abs"
```{r}
eco_long.df <- eco.df %>% 
 
  
  
  
  
  )
```


# Lets fix a few more things in the column
we want to make letter lower case   
we want to make a new column called letter_number...


```{r}
eco_long.df <- eco_long.df %>%   
  mutate(
   
    
         )
```


Here we need to make sets for the 3 replicates.     
how might you do this - think of programming and if else or case when ideas     

```{r create.sets}
eco_long.df <- eco_long.df %>% 
     # what is missing here.....
    

      number == 1 ~ "set_1",
      number == 2 ~ "set_1",
      number == 3 ~ "set_1",
      number == 4 ~ "set_1",
      number == 5 ~ "set_2",
      number == 6 ~ "set_2",
      number == 7 ~ "set_2",
      number == 8 ~ "set_2",
      number == 9 ~ "set_3",
      number == 10 ~ "set_3",
      number == 11 ~ "set_3",
      number == 12 ~ "set_3"))
```

We will do the same thing here with what is in each well... I have removed the 
key terms here so you dont know the answer above. ; )
```{r rename.wells}
eco_long.df <- eco_long.df %>% 
  # what is missing here....
  
    letter_number == "a_1" ~ "water",
    letter_number == "a_2" ~ "b_methyl_d_glucoside",
    letter_number == "a_3" ~ "d_galactonic_acid_g_lactone",
    letter_number == "a_4" ~ "l_arginine",
    letter_number == "a_5" ~ "water",
    letter_number == "a_6" ~ "b_methyl_d_glucoside",
    letter_number == "a_7" ~ "d_galactonic_acid_g_lactone",
    letter_number == "a_8" ~ "l_arginine",
    letter_number == "a_9" ~ "water",
    letter_number == "a_10" ~ "b_methyl_d_glucoside",
    letter_number == "a_11" ~ "d_galactonic_acid_g_lactone",
    letter_number == "a_12" ~ "l_arginine",
    letter_number == "b_1" ~ "pyruvic_acid_methyl_ester",
    letter_number == "b_2" ~ "d_xylose",
    letter_number == "b_3" ~ "d_galacturonic_acid",
    letter_number == "b_4" ~ "l_asparagine",
    letter_number == "b_5" ~ "pyruvic_acid_methyl_ester",
    letter_number == "b_6" ~ "d_xylose",
    letter_number == "b_7" ~ "d_galacturonic_acid",
    letter_number == "b_8" ~ "l_asparagine",
    letter_number == "b_9" ~ "pyruvic_acid_methyl_ester",
    letter_number == "b_10" ~ "d_xylose",
    letter_number == "b_11" ~ "d_galacturonic_acid",
    letter_number == "b_12" ~ "l_asparagine",
    letter_number == "c_1" ~ "tween_40",
    letter_number == "c_2" ~ "i_erythritol",
    letter_number == "c_3" ~ "hydroxy_2_benzoic_acid",
    letter_number == "c_4" ~ "l_phenylalanine",
    letter_number == "c_5" ~ "tween_40",
    letter_number == "c_6" ~ "i_erythritol",
    letter_number == "c_7" ~ "hydroxy_2_benzoic_acid",
    letter_number == "c_8" ~ "l_phenylalanine",
    letter_number == "c_9" ~ "tween_40",
    letter_number == "c_10" ~ "i_erythritol",
    letter_number == "c_11" ~ "hydroxy_2_benzoic_acid",
    letter_number == "c_12" ~ "l_phenylalanine",
    letter_number == "d_1" ~ "tween_80",
    letter_number == "d_2" ~ "d_mannitol",
    letter_number == "d_3" ~ "hydroxy_4_benzoic_acid",
    letter_number == "d_4" ~ "l_serine",
    letter_number == "d_5" ~ "tween_80",
    letter_number == "d_6" ~ "d_mannitol",
    letter_number == "d_7" ~ "hydroxy_4_benzoic_acid",
    letter_number == "d_8" ~ "l_serine",
    letter_number == "d_9" ~ "tween_80",
    letter_number == "d_10" ~ "d_mannitol",
    letter_number == "d_11" ~ "hydroxy_4_benzoic_acid",
    letter_number == "d_12" ~ "l_serine",
    letter_number == "e_1" ~ "a_cyclodextrin",
    letter_number == "e_2" ~ "n_acetyl_d_glucosamine",
    letter_number == "e_3" ~ "g_hydroxybutyric_acid",
    letter_number == "e_4" ~ "l_threonine",
    letter_number == "e_5" ~ "a_cyclodextrin",
    letter_number == "e_6" ~ "n_acetyl_d_glucosamine",
    letter_number == "e_7" ~ "g_hydroxybutyric_acid",
    letter_number == "e_8" ~ "l_threonine",
    letter_number == "e_9" ~ "a_cyclodextrin",
    letter_number == "e_10" ~ "n_acetyl_d_glucosamine",
    letter_number == "e_11" ~ "g_hydroxybutyric_acid",
    letter_number == "e_12" ~ "l_threonine",
    letter_number == "f_1" ~ "glycogen",
    letter_number == "f_2" ~ "d_glucosaminic_acid",
    letter_number == "f_3" ~ "itaconic_acid",
    letter_number == "f_4" ~ "glycyl_l_glutamic_acid",
    letter_number == "f_5" ~ "glycogen",
    letter_number == "f_6" ~ "d_glucosaminic_acid",
    letter_number == "f_7" ~ "itaconic_acid",
    letter_number == "f_8" ~ "glycyl_l_glutamic_acid",
    letter_number == "f_9" ~ "glycogen",
    letter_number == "f_10" ~ "d_glucosaminic_acid",
    letter_number == "f_11" ~ "itaconic_acid",
    letter_number == "f_12" ~ "glycyl_l_glutamic_acid",
    letter_number == "g_1" ~ "d_cellobiose",
    letter_number == "g_2" ~ "glucose_1_phosphate",
    letter_number == "g_3" ~ "a_ketobutyric_acid",
    letter_number == "g_4" ~ "phenylethylamine",
    letter_number == "g_5" ~ "d_cellobiose",
    letter_number == "g_6" ~ "glucose_1_phosphate",
    letter_number == "g_7" ~ "a_ketobutyric_acid",
    letter_number == "g_8" ~ "phenylethylamine",
    letter_number == "g_9" ~ "d_cellobiose",
    letter_number == "g_10" ~ "glucose_1_phosphate",
    letter_number == "g_11" ~ "a_ketobutyric_acid",
    letter_number == "g_12" ~ "phenylethylamine",
    letter_number == "h_1" ~ "a_d_lactose",
    letter_number == "h_2" ~ "d_l_g_glycerol_phosphate",
    letter_number == "h_3" ~ "d_malic_acid",
    letter_number == "h_4" ~ "putrescine",
    letter_number == "h_5" ~ "a_d_lactose",
    letter_number == "h_6" ~ "d_l_g_glycerol_phosphate",
    letter_number == "h_7" ~ "d_malic_acid",
    letter_number == "h_8" ~ "putrescine",
    letter_number == "h_9" ~ "a_d_lactose",
    letter_number == "h_10" ~ "d_l_g_glycerol_phosphate",
    letter_number == "h_11" ~ "d_malic_acid",
    letter_number == "h_12" ~ "putrescine",
    TRUE~"other"))
```

# Now to do the blank water correction
# https://stackoverflow.com/questions/67139356/how-to-subtract-value-of-one-group-from-other-groups-in-r
```{r}

# do water correction---

eco_long.df <- eco_long.df %>% 
 
 

```

