---
title: "R markdown notes"
author:
- affiliation: R fun time!
  affiliation_url: https://rmd4pharma.netlify.app/static/slides/02-output-tables.html#1
  name: Author?!?!?!
date: '2022-03-22'
output:   
  html_document:
    toc: true
    toc_float: true
    theme: flatly
  distill::distill_article:
    toc: true
  word_document:
    toc: true
  pdf_document: default
description: |
  Here are some notes on how to use markdown with examples
---
## above here is the metadata...in the .Rmd file
pound sign defines a header

## settings for the file
by changing inclue to false it will hide this code 
```{r setup, include=TRUE}
knitr::opts_chunk$set(
  echo = FALSE,
  warning = FALSE,
  message = FALSE,
  comment = NA)
```

# big header
## smaller header
### even smaller header

you can set the output to basically anything from a pdf to a ppt, you just define these in the output settings 

# making a list
dash before text makes a list

- tile = title,
- author = defines aithors with affiliations and a url for the author,
- date = date,
- output = the output options that you will knit to
  - toc = table of contents,
  - toc float = where the table of contents will go,
  - theme = how the file will look,
  - distill::distill_article: = specific formatting for html files 
    - the further you tab over
      - means you can make
        - sub
          - points

# Notes from markdown part 2

# note for ryan put stuff here for code and such
```{r}

```




